%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  ANDREW ANDRADE'S ACADEMIC CV
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Andrew Andrade}

\address{andrew@andrewandrade.ca} 
\address{mrandrewandrade.com}

\begin{document}

%----------------------------------------------------------------------------------------
%	 Highlights
%----------------------------------------------------------------------------------------

\begin{rSection}{Highlights}
\item Contributed to over \$10 MM dollars of value creation through product sales, cost reduction, and venture capital raising since joining co-op in highschool
\item Researcher and inventor who presented patents and academic publications internationally
\item Volunteer, mentor, motivational speaker, team builder demonstrated through various leadership roles
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Industry Experience}

%------------------------------------------------
\begin{rSubsection}{MIT \& SUTD Self Driving Vehicle Research}{Sep. 2014 - Apr. 2015}{Researcher \& Project Manager}{Singapore}

\item Lead researchers, developers and engineers at MEClab and MIT through smart.mit.edu to create a self driving, autonomous bicycle
\item Integrated probabilistic robotic system integration by building the data infrastructure  and lead the development of the sensor filtering logic
\item Conducted business model and scalability analysis using monte carlo simulation
\end{rSubsection}


\begin{rSubsection}{PetroPredict, Inc}{Sep. 2013 - Present}{Technical Co-founder and Lead Researcher}{Canada and Singapore}
\item Leading the research and technical development for the next generation of intelligent tools for the oil and gas industry
\item Created a company from just an idea to six figure total revenue in less than a year
\item Winner of 8 entrepreneurship/business competitions (over \$50,000 in funding)
\item Active contributor to student professional development and to the co-op program hiring 6 co-op students
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{ Independent Contract Work}{Sep. 2013 - Present }{Lead Consultant }{Waterloo, ON}
\item Leading the mechanical, industrial, product and manufacturing design for a wireless backhaul antenna waveguide
\item Work lead to first product in the market and was a major contributing factor to company raising \$8MM
\item Consulting included mechanical design, CAD modeling, customer specification drawings, supplier relations, outsourcing manufacturing, quality testing and validation and developing marketing material
\end{rSubsection}


%------------------------------------------------
\begin{rSubsection}{Facebook}{Jan. 2014 - Apr. 2014}{Manufacturing Engineering Co-op}{California, Oregon and China}
\item Designed and deployed hardware test fixtures in factories which lead to a \$1.4 MM hardware cost savings and additional savings in reduced energy consumption, decreased testing time and decreased worker handling
\item Drove quality issues and vendor management at Facebook's data centers, firefighting quality issues and vendor rework collaborating with American, European and Chinese vendors
\item Lead quality and manufacturing of a new server product line, a task usually given to full time engineers
\item Contributed to the Facebook campus recruitment by promoting co-op education

\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Peraso Technologies}{May 2013 - Aug. 2013}{Embedded Software Engineering Co-op}{Toronto, ON}
\item Conducted firmware and embedded development for a baseband RF Wifi Chip (MAC and PHY layer).
\item Wrote developer debug GUI and fireware features using CLI over UART, SPI and USB interfaces. 
\item Participated in board bring up and debugging using data acquisition and lab test equipment (multi-meters, oscilloscopes, power supplies)

\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Waterloo Institute for Sustainable Energy}{Jan. 2013 - Apr. 2013}{Undergraduate Research Assistant}{Waterloo, ON}
\item Completed data analysis of energy consumption and environmental indicators
\item Conducted energy policy research in context of environmental sustainability
\item Identified trends in energy consumption and environmental indicators on the global scale 
\item Dependency tested the correlation between economic motivations and energy product internationally 
\item Presented results in visually compelling forms for presentations and compendium literature

\end{rSubsection}


%------------------------------------------------
\begin{rSubsection}{TopHat}{Feb. 2013 - Mar. 2013}{Campus Ambassador}{Waterloo, ON}
\item Spearheaded adoption on campus of classroom response system with guidance from Sales and Marketing
\item Developed product awareness after establishing target audiences and business model
\item In first month closed the most demo's and received monthly award for best sales rep
\end{rSubsection}


%------------------------------------------------
\begin{rSubsection}{Suncor Energy}{Sep. 2012 - Dec. 2012}{Reservoir Engineering Co-op}{Calgary, AB}
\item Conducted a complete oil field segment analysis for redevelopment on Libyan assets using PVT, material balance, reserves estimation, and water influx calculations based on well test and production data 
\item Applied decline curve analysis and field optimization forecasting to propose redevelopment which would yield a 33\% increase in sustainable oil production using water flood and EOR techniques
\end{rSubsection}


%------------------------------------------------
\begin{rSubsection}{Imtex Membranes}{Jan. 2012 - Apr. 2012}{Mechanical Engineering Intern}{Mississauga, ON}

\item Integrated 6 $\sigma$ and lean methodologies (DMAIC and DFSS) for analytical engineering design and project feasibility leading to 45\% operating cost reduction 
\item Designed and constructed bench scale apparatus and experiment setups in a petrochemical R\&D environment
\item Developed Excel spreadsheets and other MS Office documents using macros and forms to assist researchers input data resulting in a decrease of the opportunity for data input error
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Chrysler}{Jun. 2011 - Aug. 2011}{Summer Student}{Brampton, ON}

\item Applied World Class Manufacturing continuous improvement ideals in the automotive manufacturing industry in daily part assembly and part manufacturing routines
\item Diagnosed cost of poor quality issues removing hidden factories, inherent waste and non-value added tasks by documenting ‘Quick Kaizens’ and participating in time studies
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Cantech Tool and Machine Co}{Sep. 2009 - May 2011}{Student Machinst and CNC Operator}{Mississauga, ON}
\item Operating manual and CNC milling machines, lathes and surface grinders
\item Maintained a high quality of work when machining parts with very high tolerances ($\pm$ 0.002")
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{City of Mississauga}{Aug. 2009 - May 2011}{Deck Supervisor, Lifeguard, Swimming Instructor and Camp Councilor}{Mississauga, ON}
\item Instructed leadership techniques to students in performing lifesaving methods and swimming as a First Aid and Lifesaving Instructor
\item Strengthened team building and team management resulting in no incidents or injuries while supervising
\item Demonstrated by example strong communication skills and decision making during emergency situations
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Institute for Quantum Computing}{Jul. 2010 - Aug 2010}{Summer Research Student}{Mississauga, ON}
\item Participated in the Quantum Cryptography School for Young Students (QCSYS) program.
\item Conducted hands-on experiments with lasers and group work focused on quantum cryptography
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Royal Canadian Army Cadets}{Sep. 2008 - June 2010}{Master Corporal}{Mississauga, ON}
\item Completed Army Cadet Leadership and Cadet Leadership Instructor training
\item Organized, lead and trained teams of junior cadets in basic training for outdoor skills
\item Avid drill, marksmanship, music and leadership instructor
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	PATENTS AND PUBLICATONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Patents and Publications}

\item Erik Wilhelm, Abhishek Gupta, Selvasurendhiran Modurpalayam, Rickey Wang, Brandon Walton, Adam Wootton, Tim Jeruzalski, Andrew Andrade, AutoBikes: Autonomous Electric Bicycles for First and Last-mile Mobility on Demand, The International Electric Vehicle Symposium \& Exhibition, Forthcoming

\item Andrade, A.  Multifaceted approach to oil field segment analysis using artificial intelligence,  Society of Petroleum Canadian Regional Paper Contest, August 2014

\item Andrade, A.  Growing and scaling high performance teams,  Conrad Business, Entrepreneurship and Technology Leadership Blog, August 2014

\item Fakharzadeh, M., Andrade, A., Jafarlou, S., Lynch, B., Tazlauanu, M., Waveguide adapter plate to facilitate accurate allignment of sectioned waveguide chanel in microwave antenna assembly.  U.S. Patent Application 14217683, filed March 2014. Patent Pending

\item Andrade, A. Winning a Facebook Hackathon Without a Single Line of Code, Open Compute Foundation Technical Blog, March 2014

\end{rSection}

%----------------------------------------------------------------------------------------
%	Professional Organization Leadership
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Organization Leadership}

\item Executive Member at the Society of Petroleum Engineer's Student Chapter, May 2013 - Present
\item Student Member at the Ontario Society of Professional Engineers, Sept 2011 - Present
\item Adviser at the University of Waterloo Petroleum Energy Association,  October 2013 - Present
\item VP Marketing at the University of Waterloo Petroleum Energy Association, May 2013 - September 2013
\item Adviser at the University of Waterloo Entrepreneurship Society (UWES), May 2013 - September 2013
\item Macrofabrication Lead at the University of Waterloo Nanorobotics Group, September 2012 - September 2013
\item Team Member at the University of Waterloo Nanorobotics Group, September 2011 - September 2012


\end{rSection}	



%----------------------------------------------------------------------------------------
%	AWARDS AND RECOGNITIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and Recognition}
\item Canada wide and Waterloo Engineering Co-op student of the year. March 2015

\item Third best overall  masters' research paper,  SPE Canadian Regional Paper Contest. August 2014
\item Pan IIT Global Entrepreneurship Competition Award, India Institutes of Technology.  June 2014
\item David McFadden Energy Entrepreneur Challenge, Ontario Center of Excellence. May 2014
\item Elevator Pitch Competition Award, Ontario Center of Excellence.  May 2014
\item Velocity 25k Fund, University of Waterloo.  April 2014
\item Best Use of Arduino, BeMyApp Factory Hackathon. March 2014
\item International Hackathon Winner, OpenCompute Foundation. January 2014
\item Best use of MongoDB, LAHacks. January 2014
\item Velocity 1k Fund, University of Waterloo. December 2013
\item Velocity People's Choice Award, University of Waterloo. December 2013
\item Co-op Student of the Year Honorable Mention, University of Waterloo December 2013
\item Nicol Entreprenial Award, University of Waterloo. November 2013
\item Mobile Microrobotics Winner, International Conference on Robotics and Automation. May 2013
\item Industrial Research Award, National and Engineering Research Council of Canada. May 2013
\item Undergraduate Research Award for Sustainable Energy Development, University of Waterloo. Jan 2013
\item Professional Engineers Foundation Scholarship, Professional Engineers of Ontario. June 2012
\item President Scholarship, University of Waterloo. September 2011
\item Highest Overall Average, Port Credit Secondary School.	 June 2011
\item Port Credit Alumni Excellence Award, Port Credit Secondary School. June 2011
\item Terry Garbutt Memorial Award, Port Credit Alumni Association. June 2011
\item Vice Principal Award in Technology Development, Port Credit Secondary School. June 2011
\item Ultimate Frisbee Gold Medal, Regional of Peel Sports Association. June 2011
\item Silver Medal in CNC Programming, Skills Ontario Competition. May 2011
\item Third Place Engineering Olympics, McMaster University. October 2010
\item Bronze Medal in Precision Machining, Regional Skills Ontario. May 2010
\item Fourth and Sixth Place Overall at Robotics, Skills Ontario. May 2008 \& 2009
\end{rSection}


%----------------------------------------------------------------------------------------
%	Volunteer Leadership
%----------------------------------------------------------------------------------------
\begin{rSection}{Volunteer Leadership}
\item World Community Grid Research Promotion Director and Team Captain. September 2011 - Present
\item Alumni Outreach and Motivational Speaker, Port Credit Secondary School June 2010 - Present
\item New Year's Eve Event Organizer \& Area Site Plan Manager, City of Mississauga, 2011-2012
\item Student Design Symposium Organizer, University of Waterloo, May 2012

\end{rSection}



\end{document}