\documentclass[pdftex,11pt,letterpaper]{article}

% Reduce margins to 1cm on all sides
\usepackage[margin=1cm]{geometry}

% Allow use of color names
\usepackage[usenames,dvipsnames]{xcolor}

% Enable URL linking
\usepackage{hyperref}
\definecolor{pblue}{HTML}{0395de}
\hypersetup{colorlinks=true,urlcolor=pblue}

% Customize spacing of titles
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*3}{0pt}

% Customize list spacing
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.5em,itemsep=0pt,before=\vspace{-1mm},after=\vspace{0.3mm}}

% Set font to Source Sans Pro
\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

% Modify line spacing
\linespread{0.8}

% Prevent indents for all paragraphs
\setlength{\parindent}{0pt}
\pagestyle{empty}

\title{Andrew Andrade's Manufacturing Résumé}

\begin{document}

% Ensure interword spacing in items is enough for selection and copying
\spaceskip=1.2\fontdimen2\font

\begin{center}
  {\Huge Andrew \textbf{Andrade}}

  {\large
    \href{mailto:andrew@andrewandrade.ca}{\textbf{andrew@}}\href{http://andrewandrade.ca}{andrewandrade.ca} \\ 

    \href{https://github.com/mrandrewandrade}{github.com/mrandrewandrade}\ \textperiodcentered \ \href{http://cv.mrandrewandrade.com}{\textbf{cv.mrandrewandrade.com}}\ \textperiodcentered \ \href{https://www.hackster.io/mrandrewandrade}{hackster.io/mrandrewandrade}
  }
\end{center}

\subsection*{Summary of Experience}

\begin{itemize}[before=,after=]

\item Extensive experience in manufacturing vendor mangement (ODMs, OEMs, CMs) and product validation.
  
\item Worked on multiple manufacturing design challenges and proof of concept evaluations.

\item Comprehensive rapid prototyping experience in benchtopping, machining, board creation, soldering etc.

\item Passionate about new product development and product design (and required cost comparsion modeling).

\item Strong communication and contract negotiation skills in procurement, manufacturing, testing \& distribution.

\item Analytical skills using statistics, data-mining, operations research for managerial economic evaluations.

\end{itemize}

\subsection*{Selected Professional Experience}

\href{http://facebook.com}{\textbf{Facebook Inc.}} --- Manufacturing Engineering Intern \hfill {\color{gray} California, Prineville \& China, Winter 2014}
\begin{itemize}

\item Prototyped, tested, manufactured and deployed a custom designed test fixture which lead to a $1.4 million hardware cost savings per factory, further reducing design by 8x after deploying in factories.
\item Collaborated with American, European and Chinese vendors to manufacture and assemble data center equipment.
\item Prepared customer requirement documents and conducted assembly inspections at vendors \& integrators.
\item Drove quality issues and vendor rework management at Facebook's data centers around the world.
\item Initated and lead quality and manufacturing of a new server line completing BOM revisions, and manufacturing change orders.
\item Lead transportation testing including test monitoring, shake and vibration tests for new transporation systems.
\item Audited factories in China from receiving, assembly, testing, QA, and packout/shipping areas.
\end{itemize}

\href{http://www.imtexmembranes.com/}{\textbf{Imtex Membranes Corp.}} --- Mechanical Engineering Intern \hfill {\color{gray} Mississauga, Ontario, Winter 2012}
\begin{itemize}
\item Integrated six sigma and lean methodologies (DMAIC and DFSS) for analytical engineering design and project feasibility.
\item Designed and constructed bench scale apparatus and experiment setups in a manufacutring R\&D environment.
\item Collected and translated production trend data into improved standard operating procedure guidelines.

\end{itemize}

\href{http://chrysler.ca}{\textbf{Chrysler}} --- Manufacturing Summer Student \hfill {\color{gray} Brampton Assembly Plant, Summer 2011}
\begin{itemize}
\item Diagnosed cost of poor quality issues by removing hidden factories, inherent waste and non-value added tasks.
\end{itemize}

\href{http://atmshop.ca/}{\textbf{All-Type Machine Shop}} --- Mechanical Designer and CNC Programmer \hfill {\color{gray} Mississauga, Ontario, Summer 2010}
\begin{itemize}
\item Designed machine tooling and plastics molds for automotive industry suppliers.
\end{itemize}

\textbf{Cantech Tool and Machine Shop} --- Summer Machinist \hfill {\color{gray} Mississauga, Ontario, Summer 2009}
\begin{itemize}
\item Operated manual machines, polished parts, filed and swept floors.
\end{itemize}
  
\subsection*{Selected Consulting Experience}

\href{http://www.haloculturecanada.com/collections/titanium-flash-edc}{\textbf{Militia Everyday Carry Co.}} --- Manufacturing and Industrial Design Consulting \hfill {\color{gray} Toronto, Summer 2014}
\begin{itemize}
  \item Lead new Titanium product line launch from industrial and product design to procurement (sourcing \& manufacturing).
\end{itemize}

\href{http://www.perasotech.com/}{\textbf{Peraso Semiconductor Technologies}} --- Mechanical Manufacturing Lead, \hfill {\color{gray} Toronto, Fall 2013}
\begin{itemize}
  \item Industrial antenna product design, CAD modeling, customer specification drawings, manufacturing and validation.
  \item Built Peraso’s supply chain from the ground up and created best practices, now used by company.
  \item Work lead to first product in the market antenna and was a major contributing factor to company raising \$8MM round.
\end{itemize}

\subsection*{Patent}
Waveguide adapter plate to facilitate accurate alignment of sectioned waveguide channel in microwave antenna assembly \color{gray} {M. Fakharzadeh, \textbf{A. Andrade}, S. Jafarlou, B. Lynch, and M. Tazlauanu} \hfill {\color{gray} Patent Pending}
\color{black}

\subsection*{Education}
Candidate for BASc in \textbf{Mechatronics Engineering} \hfill {\color{gray} University of Waterloo, 2011 -- 2016 (expected)}
\begin{itemize}
  \item Minor in \textbf{Management Sciences}, Focus: Operations Research, Supply Chain Management, Managerial Economics.
\end{itemize}

\subsection*{Tools and Technology}
\textbf{Design:} Solidworks, Unigraphics NX, MasterCAM, AutoCAD, Matlab, Simulink, MultiSim, Cadence/Allegro \\
\textbf{Programming:} C/C++, Python, R, Java, Tableau, Tibco, HTML5/CSS, SQL, Windows/Linux/Mac/Android\\
\textbf{Manufacturing} PCBa, SMT, CNC/Manual Mill, Lathe, Surface Grinder, MIG/TIG/ARC Welding, 3D Printing, Soldering \\
\textbf{Debug Tools:} Spectrum analyzer, Power meter, Oscilloscopes, Probes, Logic Analyzers, Microscopes, JTAG\\
\textbf{Testing:} GD\&T (automated caliper), Six Sigma (DMAIC), DOE, DFT/DFM, ISO 9000 , AOI / AXI/ 5DX , ICT/ BFT/IST/SAT
\end{document}
